Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-10 paper/main.tex
Updates

We analyzed the performance of \textsc{ExpertInLoop} algorithm by comparing it
with three other automated algorithms: PC, Hill-Climb Search, and Greedy
Equivalence Search (GES). For the analysis, we simulated data from known DAGs
and use the algorithms to recover the original DAG. We start by generating a
random DAG on $10$ nodes and use linear models with random effects to simulate
$ 500 $ samples from it. We simulate each variable $ Y_i $ in the DAG as:

\begin{equation}
	\begin{split}
		\beta &= \mathrm{Uniform}([-0.6, 0.6]) \\
		Y_i &= \bm{\beta} \mathrm{Pa}_G(Y_i) + \mathcal{N}(0, 1)
	\end{split}
\end{equation}

@@

\section{Conclusions}

Points:
\begin{itemize}
	\item As researchers prefer to build models by hand, we present a tool
		to assist them in construction using CI testing.
	\item In practice as many edges are possible for any given DAG, we provide
		a ranking method to find the best edge addition.
	\item Compared to other expert knowledge specification methods, users
		don't need to guess what information then need to provide as
		exact questions are asked. Also enables us to ask an LLM for
		it.
\end{itemize}

Future work:
\begin{itemize}
	\item Add latent variables; extend to ADMGs.
	\item Can potentially be combined with pairwise orientation methods.
	\item Improvements in the web-interface.
\end{itemize}

\bibliography{references}

>>>>

We analyzed the performance of \textsc{ExpertInLoop} algorithm by comparing it
with three other automated algorithms: PC, Hill-Climb Search, and Greedy
Equivalence Search (GES). For the analysis, we simulated data from known DAGs
and use the algorithms to recover the original DAG. We start by generating a
random DAG on $10$ nodes and use linear models with random effects to simulate
$ 500 $ samples from it. We simulate each variable $ V_i $ in the DAG as:

\begin{equation}
	\begin{split}
		\beta &= \mathrm{Uniform}([-0.6, 0.6]) \\
		V_i &= \bm{\beta} \mathrm{Pa}_G(V_i) + \mathcal{N}(0, 1)
	\end{split}
\end{equation}

@@

\section{Conclusions}
Researchers often prefer to construct DAGs manually rather than using automated
algorithms due to practical challenges in applying automated methods. To assist
in the process, we developed an iterative structure learning method that
integrates manual construction with data-driven insights. This approach bridges
the gap between fully manually and fully automated methods by providing a
systematic way to construct DAGs while utilizing data.

In future we would like to extend our approach to latent variables and Acyclic
Directed Mixed Graphs (ADMGs), explore the potential of combining our approach
with pairwise orientation methods. We would also improve the web interface for
better usability. 
\bibliography{references}
